\section{Chapter II - Membership and Governance}

~

~

\large{\textbf{Article 5 - Membership}}

~

\underline{Paragraph A} - Full membership will be open to all registered
students at the University of Glasgow. Full membership shall expire on the first day of the first
semester following completion or termination of studies.

~

\underline{Paragraph B} - Students registered at other universities or
other individuals interested in The Society will be able to join as
Associate Members if their application is approved by the Executive Board.
Such a membership runs until revoked by the Executive Board. 
Associate Members do not have the right to vote in the annual group meeting 
or in an emergency group meeting.

~

\underline{Paragraph C} - Every member is obliged to sign the
Declaration of Responsibility as provided by The School of Computing
Science in order to be allowed access to the School's facilities.

~

\underline{Paragraph D} - Associate members shall not account for more
than 20\% of the total membership number.

~

~

\large{\textbf{Article 6 - Governance}}

~

\underline{Paragraph A} - The Society shall be under the control of the
membership. As such, all full members of The Society shall have the
right to elect their representatives for the available positions in the
Executive Board.

~

\underline{Paragraph B} - The Society shall have five office bearers,
forming the Executive Board:\\
President, Vice President, Secretary, Treasurer, and General Board Member.

~

\underline{Paragraph C} - The Committee shall consist of the Executive
Board of The Society, former members of the Executive Board, and the
organising committee.

\underline{Paragraph D} - The organising committee are those who help
organise The Society's events.

~

\underline{Paragraph E} - All members of the Committee shall either be
registered students at the University of Glasgow, or
alumni of the University of Glasgow. Only membership of the committee who 
are currently a registered student will qualify to run for the Executive
Board.

~

~

\large{\textbf{Article 7 - Executive Board and Responsibilities}}

~

\underline{Paragraph A} - Concerning all members of the Executive Board:

\begin{itemize}

    \item{Members of the Executive Board shall decide who has the right to access The Society’s bank account}

    \item{Members or the membership of The Society shall obtain previous approval from the Executive Board in order to use the name, resources and image of The Society.}

    \item{Members shall approve the creation of special interest groups based on critical mass, an indication of support for the group and checks on any ethical issues.}

    \item{The Executive Board shall decide annually which groups will persist into the new academic year based on attendance at meetings and evidence of progress.}

    \item{Members shall attend all Executive Board meetings. If a member is not able to attend the meeting, said member must notify the President or Vice President at least 24 hours in advance.}

    \item{Members are responsible for maintaining and improving the image of The Society through their actions and behaviour.}

    \item{A member's position in the Executive Board shall be taken into discussion at the Executive Board meeting if a member is absent for two consecutive Executive Board meetings or one AGM or EGM without prior approval of the President or the Vice President.}

    \item{A member's position in the Executive Board shall be taken into discussion if a member does not comply with their responsibilities or acts against the interests of The Society.}

    \item{Discussions concerning a member's position in the Executive Board must have a 50\% plus one support from the rest of the Executive Board members and must be corroborated with at least one of the above points regarding their responsibilities and actions.}

    \item{Any member of the Executive Board can be removed from their position with the approval of two-thirds of the Executive Board.}

    \item{Any vacancy that may occur in an office shall be filled by an Extraordinary General Meeting, an eligible member shall be elected to serve the remainder of the term. }

\end{itemize}

~

\underline{Paragraph B} - \textbf{The President} shall:

\begin{itemize}

    \item{Be the spokesperson for The Society.}

    \item{Be the point of contact to the School of Computing Science.}

    \item{Convene and chair the meetings of the Executive Board and the Committee unless unavailable.}

    \item{Coordinate the work and activities of the Executive Board and the Committee.}

    \item{Provide directions to the activities of all Executive Board members.}

\end{itemize}

~

\underline{Paragraph C} - \textbf{The Vice President} shall:

\begin{itemize}

    \item{Assume the duties of the President should the office become vacant, or in the absence of the President.}

    \item{Assist other members of the Executive Board and the Committee in completing their jobs.}

    \item{Act as the parliamentarian for The Society.}

    \item{Provide feedback to The Society regarding its operations and functioning.}

    \item{Be the President's advisor in any important decisions.}

\end{itemize}

~

\underline{Paragraph D} - \textbf{The Secretary} shall:

\begin{itemize}

    \item{Keep minutes of AGMs, EGMs, and general Executive Board and Committee meetings.}

    \item{Notify the President of vacant board roles.}

    \item{Consider if the Executive Board is achieving the objectives defined in this constitution.}

    \item{Assist the Vice President in completing their job.}

\end{itemize}

~

\underline{Paragraph E} - \textbf{The Treasurer} shall:

\begin{itemize}

    \item{Maintain a record of the income and expenditure of The Society.}

    \item{Prepare the accounts and keep up to date bank statements.}

    \item{Prepare a detailed report of all financial activities of The Society and present it in all AGMs or upon request in an EGM or at an Executive Board meeting.}

    \item{Disburse money to other members of the Executive Board for authorised uses.}

\end{itemize}

~

\underline{Paragraph F} - \textbf{The General Board Member}
shall:

\begin{itemize}

    \item{Overlook outreach of The Society.}

    \item{Make information regarding helping at events available.}

    \item{Assist other Executive Board members in their duties.}

\end{itemize}
