\section{\underline{Chapter I - Overview}}

~

~

\large{\textbf{Article 1 - Name}}

~

The name of the society shall be `Glasgow University Tech Society'
(hereafter referred to as `The Society') and shall be abbreviated as
GUTS.

~

~

\large{\textbf{Article 2 - Equal Opportunities}}

~

The Society will comply with the University's policies, including
policies on equal opportunities.
The Society shall promote equal opportunities, whatever a person's race, colour, ethnic or national origin, religion, beliefs, political positions, sex, sexual orientation, gender identity, HIV status, age, physical or mental disability, state of health, appearance, status, and family circumstances 
The Society will also be committed to accommodating those with special
needs.

~

~

\large{\textbf{Article 3 - Objectives}}

~

The Society's objectives shall be:

~

\underline{Paragraph A} - To offer students the opportunity to develop
leadership and networking skills.

~

\underline{Paragraph B} - To create a platform for software and hardware
development, IT start-ups and tech enterprise.

~

\underline{Paragraph C} - To broaden interest in Computing Science and
related disciplines

~

\underline{Paragraph D} - To introduce students to team programming and
its management.

~

\underline{Paragraph E} - To promote the open-source movement.

~

\underline{Paragraph F} - To collaborate on technology related projects
in areas such as web development, mobile development, open hardware,
scientific modelling, security and cryptography, and game development,
among others.

~

~

\large{\textbf{Article 4 - Activities}}

~

The Society will achieve its objectives and purposes through the
following activities. Such activities should be open to all
its members, and in special circumstances, to the wider public.
Special circumstances such as Government imposed lockdowns or 
other reasonable exceptions may release the Society 
from these commitments.


~

\underline{Paragraph A} - An annual Hackathon.

~

\underline{Paragraph B} - An annual ball.

~

\underline{Paragraph C} - Creating special interest groups to
collaborate on technology-related projects.

~

\underline{Paragraph D} - An annual introductory event for first year
students.

~

\underline{Paragraph E} - Events and projects in collaboration with
other societies at the University of Glasgow.